### 2011-11-09 doc/theses/mikula/proposed_algorithm.tex
Master thesis: In progress.

\subsection{Analysis of Expressions}
\todo[inline]{Je nutne analyzovat aj typy deklarovanych premennych, kedze tie sa mozu pouzivat vo vyrazoch.}

>>>>

\subsection{Determination of Expression Types}
\todo[inline]{VYRIESIT: external variables, scope and visibility of variables - ako si udrziavat}

\begin{algorithm}
\caption{Function analysisOfExpressionTypes}
\label{ALG_func_analysisOfExpressionTypes}
\begin{algorithmic}[1]
\REQUIRE{\ \\
    $startingNode$: A node determinig a subtree to perform the analysis on \\
    $contextVarTypes$: Types of local variables valid in the current subtree.
}

\FORALL{$subnode \in$ all subnodes of $startingNode$}
    \STATE $analysisOfExpressionTypes(subnode, contextVarTypes)$ \COMMENT{recursion}
    \IF{$subnode$ defines new variables valid for following subnodes}
        \STATE $newVarTypes = subnode.variableTypes$
        \STATE TODO rozsir context
    \ENDIF
\ENDFOR
\IF{$startingNode$ is expression node}
    \STATE $startingNode.type = determineExpressionType(startingNode)$
\ENDIF
\IF{$startingNode$ defines new variables valid in the supernode}
    \STATE TODO spracuj variables
    \STATE memorize their types in $startingNode.variableTypes$
\ENDIF
\end{algorithmic}
\end{algorithm}

\begin{algorithm}
\caption{Determination of an Expression Type in Query Body}
\label{ALG_determination_of_an_expression_type_in_query_body}
\begin{algorithmic}[1]
\REQUIRE{\ \\
    $exprNode$: An expression node in the syntax tree. \\
    $contextVarTypes$: Types of local variables valid in the current context.
}
\ENSURE The expression type.

\STATE $type = null$
\IF{$exprNode$ represents a literal value}
     \STATE $type =$ particular literal value type
\ELSIF{$exprNode$ represents a call of function $f$}
     \STATE $type = getFunctionReturnType(f)$
\ELSIF{$exprNode$ represents variable reference $var$}
     \STATE $type = getVariableType(contextVarTypes, var)$
\ELSIF{$exprNode$ represents path expression $path$}
     \STATE $type = TODO$
\ELSIF{$exprNode$ represents operator $op$}
     \STATE TODO
\ELSIF{$exprNode$ represents $FLWOR$ construct $flwor$}
     \STATE $contextVarTypes = contextVarTypes + getFLWORVarTypes(flwor)$
     \STATE
\ENDIF
